---
title: "Data 606 Project"
author: "Johnny Rodriguez"
date: "2022-11-6"
output:
  html_document:
    code_folding: show
    toc: true
    toc_float:
      collapsed: true
    toc_depth: 4
    number_sections: false
    highlight: pygments
    theme: cerulean
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE ,warning = FALSE, message = FALSE)

```


### Data Preparation & Description
The dataset consists of IT support tickets for a small liberal arts college in NYC.  The IT support tickets encompass technical, computer, software and access issues for students, faculty and staff for the full year 2021 through Nov 4, 2021.  This covers one full academic year Aug 2021 - June 2022 (fall and spring).   Columns that identify the college and its students and employees have been removed.

```{r}

#Libraries
library(tidyverse)
library(lubridate)
library(psych)
library(ggplot2)
library(scales)

#Load the data
it_support_tix <- read.csv("https://raw.githubusercontent.com/johnnydrodriguez/data606project/main/IT_Tickets_2022_2021.csv", na.strings=c("","NA"))

#Converts character date column into dates
it_support_tix$resolved_at <- mdy_hm(it_support_tix$resolved_at)
it_support_tix$opened_at <- mdy_hm(it_support_tix$opened_at)

#Calculates the ticket age (date resolved - date opened)
it_support_tix <- it_support_tix %>% 
  mutate(age_at_resolution_days =  round(difftime(it_support_tix$resolved_at, it_support_tix$opened_at, units = "days"), digits = 2))

#To create summary statistics, the age_at_resolution is converted to numeric
it_support_tix$age_at_resolution_days <- as.numeric(it_support_tix$age_at_resolution_days)

glimpse(it_support_tix)


```


### Research question 
Does the Contact type (the method the user first initiates the support ticket) predict the age of ticket at resolution?

Why this matters to IT operations managers:  IT support principles typically promote resolution on first contact over the shortest period of time until resolution. IT operations managers will attempt to funnel requests into contact channels that allow IT analysts to resolve issues as quickly as possible.

### Cases 

Each case represents an IT support incident  ie, a user has been affected by a technical issue that needs to be resolved.  There are 14,069 cases and 12 variables.



### Data collection 

Each incident is either system-generated when the IT support request is made through email or the self service portal.  A support ticket is manually created by an IT analyst when a user makes a support request via phone or walks into the support office.



### Type of study 

This is an observational study.



### Data Source 

The data is exported from an IT support database which stores data on each support interaction.




### Dependent Variable

The dependent variable is ticket age (in days) until resolution (date resolved - date created).  This value is numeric.



### Independent Variable(s)

The independent variable is the contact type - ie, one of 4 methods the user can use to initiate a support requests: email, phone, walk-in, self-service.


### Relevant summary statistics 
The distribution of the age at resolution is heavily skewed to the right.  Analysis that depends on normal distribution approximations may not be possible. 

```{r}

# Summary stats of the age at resolution
describe(it_support_tix$age_at_resolution_days)

# More Summary stats of the age at resolution
summary(it_support_tix$age_at_resolution_days)

#Proportional table of suppport tickets by the contact type
prop.table(table(it_support_tix$contact_type, useNA='ifany')) * 100


# Summary stats of age at resolutions grouped by the contact type
describeBy(it_support_tix$age_at_resolution_days, 
           group = it_support_tix$contact_type, mat=TRUE)

# Distribution of tickets by age at resolution
ggplot(it_support_tix, aes(x=age_at_resolution_days)) + geom_histogram(binwidth = 20)

```

